Convective penetration probably parameterizes convective overshoot

### 2021-07-23 manuscript/ms.tex
updates paper after final comb-through

\begin{figure}[t!]
\centering
\includegraphics[width=\columnwidth]{theory_profiles.pdf}
\caption{
Temporally- and horizontally-averaged profiles in an evolved simulation from the kinetic energy equation (Eqn.~\ref{eqn:kinetic_energy_1D}).
The vertical dashed line corresponds to the Schwarzschild CZ boundary, the vertical solid line corresponds to the top of the PZ.
(upper) Kinetic energy fluxes $\bar{\mathcal{F}}$, which go to zero at the bottom boundary and the top of the PZ.
(bottom) Source terms from Eqn.~\ref{eqn:kinetic_energy_1D} normalized by the maximum of $\overline{\mathcal{B}}$ ($\bar{\mathcal{F}}$ in the upper panel is similarly normalized).
The buoyancy source $\bar{\mathcal{B}}$ changes sign at the Schwarzschild boundary, and $\bar{\Phi}$ is positive-definite.
\label{fig:theory_profiles}
}
\end{figure}

@@

The average convective velocity depends on the magnitude of the convective flux, $\angles{\vec{|u|}} \approx F_H^{1/3} = (Q_{\rm{mag}}\Delta_H)^{1/3}$.
The characteristic convective frequency is ${f_{\rm{conv}} = \angles{\vec{|u|}} / L_s}$.
Empirically we find that for our choice of parameters, $\angles{\vec{|u|}} \approx 1$, and so going forward we define ${u_{\rm{ff}} \approx 1}$ and $f_{\rm{conv}} \approx 1$.
The stiffness is defined,
\begin{equation}
\mS \equiv \frac{N^2}{f_{\rm{conv}}^2} \approx N^2,
\label{eqn:stiffness}
\end{equation}
where $N^2$ is the \brunt$\,$frequency in the radiative zone.
In our nondimensionalization, $N^2 = \gradad - \gradrad$.
We use $\mS$ as a control parameter.

Aside from $\mS$ and $\mP$, the two remaining control parameters $\mR$ and $\Pran$ determine the properties of the turbulence.
The value of $\mR$ roughly corresponds to the value of the Reynolds number $\rm{Re} = \mR |\vec{u}|$, and we set the ratio of the diffusivities $\Pran = 0.5$ throughout this work.
Astrophysical convection is in the limit of $\Pran \ll 1$ \citep{garaud2021}; we choose a modest value of $\Pran$ which slightly separates the scales between thermal and viscous structures while still allowing us to achieve convection with large Reynolds and P\'{e}clet numbers.

\subsection{Case I: Discontinuous flux}
Most of the simulations in this paper have a discontinuous convective flux at the Schwarzschild convective boundary.
We achieve this by constructing a discontinuous radiative conductivity,
\begin{equation}
k = \begin{cases}
k_{\rm{CZ}}	&	z < 1 \\
k_{\rm{RZ}} &	z \geq 1
\end{cases},
\label{eqn:sim_discontinuous_k}
\end{equation}
where CZ refers to the convection zone and RZ refers to the radiative zone (some of which will be occupied by the penetrative zone PZ).
Using $\mS$ and $\mP_D$ as inputs and specifying the radiative flux at the bottom boundary and in the RZ defines this system\footnote{
We solve the system of equations $\mS = (\gradad - \gradrad)/f_{\rm{conv}}^2$, $\mP = F_H/(k_{\rm{RZ}}[\gradad - \gradrad])$, $F_{\rm{bot}} = k_{\rm{CZ}}\gradad$, and ${F_{\rm{bot}} + F_H = k_{\rm{RZ}}\gradrad}$ to arrive at Eqn.~\ref{eqn:discontinuous_constants}
In the dimensional equations, $N^2 = |\alpha| g (\gradad - \gradrad)$, but we have nondimensionalized out the $\alpha$ and $g$.
},
\begin{equation}
\begin{split}
&k_{\rm{RZ}} = \frac{F_H}{f_{\rm{conv}}^2\mS\mP_D},\\
&k_{\rm{CZ}} = k_{\rm{RZ}}\frac{\mu}{1 + \mu + \mP_D^{-1}},\\
&\gradad = f_{\rm{conv}}^{2}\mS\mP_D(1 + \mu + \mP_D^{-1}),\\
&\gradrad = \gradad - f_{\rm{conv}}^{2}\mS.
\label{eqn:discontinuous_constants}
\end{split}
\end{equation}

@@

\subsection{Case II: Piecewise linear flux}
We also study simulations where the flux's gradient may be discontinuous at the Schwarzschild convective boundary.
We achieve this by constructing a radiative conductivity with a piecewise discontinuous gradient,
\begin{equation}
\partial_z k = \partial_z k_0
\begin{cases}
1	&	z < 1 \\
\mP_L^{-1} &	z \geq 1
\end{cases}
\label{eqn:sim_linear_k}
\end{equation}
Since $k$ varies with height, formally the values of $\mS$ and $\mP$ also vary with height; we specify their values at $z = 2$.
By this choice\footnote{
We solve the system of equations where ${k_{\rm{bot}}\gradad = F_{\rm{bot}}}$, ${k_{\rm{ad}}\gradad = F_{\rm{bot}} + F_H}$, ${k_{\rm{ad}} = k_{\rm{bot}} + \partial_z k_0 L_s}$, ${\mS = (\gradad - \justgrad_{\mathrm{rad},z=2L_s})/f_{\rm{conv}}^2}$, and ${\gradrad = F_{\rm{tot}}/k(z)}$.
}, we require
\begin{equation}
\partial_z k_0 = \frac{F_{H}}{f_{\rm{conv}}^2L_s \mS \psi},\,\,
k_b = \frac{F_H \mu}{f_{\rm{conv}}^2\mS\psi},\,\,
\gradad = f_{\rm{conv}}^2 \mS \psi,
\end{equation}
where $\psi \equiv 1 + \mP_L(1 + \mu)$.
We will study one sweep through $\mP_L$ space at fixed $\mR$ and $\mS$.
According to Eqn.~\ref{eqn:linear_prediction}, we expect $\delta_p \propto \mP_L^{1/2}$.

@@

\begin{figure*}[t]
\centering
\includegraphics[width=\textwidth]{time_evolution.pdf}
\caption{
(left top panel) The PZ height $\delta_{0.5}$ vs.~time.
We also show the time evolution of $f$ (left middle panel, defined in Eqn.~\ref{eqn:f_defn}) and $\xi$ (left bottom panel, defined in Eqn.~\ref{eqn:xi_defn}).
The vertical lines denote the times at which the traces first converge to within 1\% of their final values, which are denoted by solid horizontal lines.
(right panel) The vertical profile of $\justgrad/\gradad$ is plotted against height at regular time intervals.
The line color denotes the time, following the time traces in the left panels.
The constant value of $\gradad$ is denoted by the horizontal dashed grey line, and the value of $\gradrad$ is denoted by the solid grey line.
The location of the Schwarzschild convective boundary is displayed as a vertical dashed black line and denotes the place where $\gradad = \gradrad$.
The top-of-PZ departure points (Eqn.~\ref{eqn:delta_p_measures}) are plotted over the profile evolution ($\delta_{0.1}$ and $\delta_{0.9}$ as red lines, $\delta_{0.5}$ as black lines).
\label{fig:time_evolution}
}
\end{figure*}

@@

\begin{figure*}[t]
\centering
\includegraphics[width=\textwidth]{parameters_vs_p.pdf}
\caption{
Results from simulations with a Schwarzschild boundary characterized by a discontinuous conductivity (left, Case I, $k$ defined by Eqn.~\ref{eqn:sim_discontinuous_k}) and with a discontinuous conductivity gradient (right, Case II, $k$ defined by Eqn.~\ref{eqn:sim_linear_k}).
The top panels show the penetration height according to Eqn.~\ref{eqn:delta_p_measures}.
The Case I penetration heights (upper left) vary linearly with $\mP$, in line with the prediction of Eqn.~\ref{eqn:discontinuous_prediction}.
The Case II penetration heights (upper right) vary like $\sqrt{\mP}$, in line with the prediction of Eqn.~\ref{eqn:linear_prediction}.
In the middle panels, we measure $f$ according to Eqn.~\ref{eqn:f_defn}.
We find values of $f \in [0.5, 0.9]$, and changes in $f$ are secondary to changes in $\mP$ for determining penetration heights.
In the bottom panels, we measure $\xi$ according to Eqn.~\ref{eqn:xi_defn}.
We find characteristic values of $\xi \in [0.5, 0.75]$, suggesting that the falloff of the $\bar{\Phi}$ in the PZ is well described by a linear function (at high $\mP$ when $\xi = 1/2$), or by a cubic function (at low $\mP$ when $\xi \approx 3/4$).
\label{fig:parameters_vs_p}
}
\end{figure*}

@@

We now describe the results of the 3D dynamical simulations described in the previous section.
Dynamics in these simulations resemble those previously shown in Fig.~\ref{fig:vertical_dynamics_panels}.
To quantitatively compare our simulations to the theory of Sec.~\ref{sec:theory}, we will present time- and volume-averaged scalar quantities, as well as some select horizontally-averaged vertical profiles.

@@

%\begin{figure*}[t]
%\centering
%\includegraphics[width=\textwidth]{vertical_dynamics_panels.pdf}
%\caption{
%Displayed is an instantaneous snapshot of dynamics in a vertical slice through the simulation with $\mR = 6.4 \times 10^3$, $\mP_D = 4$ and $\mS = 10^3$.
%In both panels, the nominal Schwarzschild boundary of the convection zone where $\gradad = \gradrad$ is displayed as a dashed horizontal line, and the top of the penetrative zone ($\delta_{0.1}$) is shown by a solid horizontal line.
%(Left) The vertical velocity is shown; orange convective upflows extend far past the Schwarzschild boundary of the convection zone but stop abruptly where $\justgrad$ departs from $\gradad$.
%(Right) Temperature fluctuations are shown, normalized by their average magnitude at each height in order to clearly display all dynamical features.
%Unlike the vertical velocity, $T'$ shows distinctly different behavior in the CZ and PZ, switching sign at the Schwarzschild boundary of the convection zone.
%\label{fig:vertical_dynamics_panels}
%}
%\end{figure*}

In Fig.~\ref{fig:time_evolution}, we show the time evolution of a Case I (discontinuous conductivity) simulation with $\mR = 400$, $\mS = 10^3$, and $\mP_D = 4$ whose temperature profile has $\justgrad = \gradad$ in the convection zone ($z \lesssim 1$) and $\justgrad = \gradrad$ in the radiative zone ($z \gtrsim 1$).
In the top left panel, we display the height of the penetrative region $\delta_{\rm{0.5}}$ vs.~time.
This region initially grows quickly over hundreds of freefall times, but this evolution slows down; reaching the final equilibrium takes tens of thousands of convective overturn (freefall) times.
The evolution of the other parameters in our theory ($f$, $\xi$) are shown in the middle and bottom left panels of Fig.~\ref{fig:time_evolution}.
We plot their rolling mean, averaged over 200 freefall time units. 
We see that the values of $f$ and $\xi$ reach their final values ($f \approx 0.67$, $\xi \approx 0.58$) faster than the penetration zone evolves to its full height.
We quantify this fast evolution by plotting a vertical line in each of the left three panels corresponding to the first time at which the rolling average converges to within 1\% of its final value (averaged over the final 1000 freefall times of the simulation and plotted as a grey horizontal line).
The evolved value of $f$ indicates that roughly 2/3 of the buoyancy driving is dissipated in the bulk CZ, so that 1/3 is available for PZ dissipation and negative buoyancy work.
The evolved value of $\xi$ indicates that the shape of dissipation in the PZ is slightly steeper than linear.

In the right panel of Fig.~\ref{fig:time_evolution}, we plot the profile of $\justgrad/\gradad$ in our simulation at regular time intervals, where the color of the profile corresponds to time, as in the left panels.
$\gradad$ is plotted as a dashed horizontal line while $\gradrad$ is plotted as a grey solid line which decreases with height around $z \approx 1$ and satures to a constant above $z \gtrsim 1.1$.
The location of the Schwarzschild boundary, $L_s$, is overplotted as a black vertical dashed line and does not evolve over the course of the simulation.
We note that the Schwarzschild boundary does not move over the course of our simulation, so the extention of the convection zone past this point is true penetration and not the result of entrainment-induced changes in the Schwarzschild (or Ledoux) convective boundaries.
The traces of $\delta_{0.1}$ and $\delta_{0.9}$ are plotted as red lines while that of $\delta_{0.5}$ is plotted as a black line.
We see that the fast initial evolution establishes a sizeable PZ (denoted by purple $\justgrad$ profiles), but its final equilibration takes much longer (indicated by the separation between the purple, green, and yellow profiles decreasing over time).
%This occurs in part because the flattening of $\justgrad < \gradrad$ above the penetrative zone increases the effective value of $N^2$ and thus the stiffness at the PZ-RZ boundary; however, this long evolution occurs on timescales similar to the thermal diffusion time in the RZ.

This long evolution is computationally expensive; for this modest simulation (256x64$^2$ coefficients), the evolution represents roughly 20 days of evolution on 1024 cores for a total of $\sim$500,000 cpu-hours.
It is not feasible to perform simulations of this length for a full parameter space study, and so we accelerate the evolution of most of the simulations in this work.
To do so, we take advantage of the nearly monotonic nature of the evolution of $\delp$ vs.~time displayed in Fig.~\ref{fig:time_evolution}.
We measure the instantaneous values of $(\delta_{0.1}, \delta_{0.5}, \delta_{0.9})$, as well as their instantaneous time derivatives.
Using these values, we take a large ``time step'' forward, advancing the values of $\delp$ according to their current trend.
While doing so, we preserve the width of the transition from the PZ to the RZ, and we also adjust the solution so that $\justgrad = \gradrad$ in the RZ, effectively equilibrating the RZ instantaneously.
In other words, we reinitialize the simulation's temperature profile with a better guess at its evolved state based on its current dynamical evolution.
For details on how this procedure is carried out, see Appendix \ref{app:accelerated_evolution}.

%In Fig.~\ref{fig:vertical_dynamics_panels}, we display instantaneous vertical slices through a turbulent simulation with $\mR = 6.4 \times 10^3$, $\mP_D = 4$ and $\mS = 10^3$ with a coefficient resolution of 384$^3$ in an equilibrated state (this is the same $\mP_D$ and $\mS$ as in Fig.~\ref{fig:time_evolution}, but higher $\mR$).
%We see that strong convective dynamics (viewed in the left vertical velocity panel) extend beyond the Schwarzschild boundary of the convection zone (horizontal dashed grey line) into a penetration zone.
%Above the PZ, there is a dynamically distinct stable radiative zone with negligible vertical velocity (above the solid horizontal line).
%On the right, we see that hot upwellings in the convection zone are turned into cold upwellings in the PZ as a result of effective cooling from the sharp change in $k$ around the Schwarzschild boundary of the convection zone.
%These upwellings impinge upon the stable radiative zone and excite gravity waves, but our focus in this work is on the nature of the PZ where convective velocities and temperature anomalies are generally oppositely signed.

\begin{figure*}[t]
\centering
\includegraphics{parameters_vs_s.pdf}
\caption{
(Left panel) Penetration heights are shown as a function of stiffness for simulations with a discontinuous conductivity.
While the width of the transition layer from the adiabatic PZ to the stable RZ shrinks as a function of $\mS$, the mean penetration height ($\delta_{0.5}$) is roughly constant.
(Right panel) The width of the thermal transition layer ($\delta_{0.9} - \delta_{0.1}$) is shown as a function of stiffness.
We roughly observe a $\mS^{-1/2}$ scaling, similar to that expected by e.g., \citet{korre_etal_2019}.
\label{fig:parameters_vs_s}
}
\end{figure*}

\subsection{Dependence on $\mP$}
We find that the height of the penetration zone is strongly dependent on $\mP$.
In the upper two panels of Fig.~\ref{fig:parameters_vs_p}, we plot the penetration height ($\delta_{0.1}$, $\delta_{0.5}$, $\delta_{0.9}$ from Eq.~\ref{eqn:delta_p_measures}) from Case I simulations (discontinuous $k$, upper left) and Case II simulations (discontinuous $\partial_z k$, upper right).
The fixed values of $\mR$ and $\mS$ are shown above these panels.
We find that the leading-order $\mP$ scaling predictions of Eqns.~\ref{eqn:discontinuous_prediction} \& \ref{eqn:linear_prediction} describe the data extremely well (orange lines).
At small values of $\mP$ we see somewhat weaker scalings than these predictions, because the profiles of $k$ and $\partial_z k$ are not truly discontinuous but jump from one value in the CZ to another in the RZ over a finite width (see e.g., the $\gradrad$ profile in Fig.~\ref{fig:time_evolution} \& Sec.~\ref{sct:numerics}).
At large values of $\mP$, penetration height falls off of these predicted scaling laws.
In this regime, dissipation dominates over buoyancy in the PZ and PZ heights saturate.

The middle and bottom panels of Fig.~\ref{fig:parameters_vs_p} demonstrate that that $f$ and $\xi$ are to leading order constant with $\mP$.
However, we find that $f$ has slightly smaller values in the Case I simulations (left) than in the Case II simulations (right).
We measure characteristic values of $f \in [0.6, 0.9]$, signifying that 60-90\% of the buoyant work is balanced by dissipation in the convection zone, depending on the simulation.
We note a weak trend where $f$ decreases as $\mP$ increases.
As $\mP$ incraeses, we find that CZ velocities decrease, leading to a decrease in the dissipation rate.
When $\mP$ is small, the PZ-RZ boundary (which acts like a wall, left panel of Fig.~\ref{fig:vertical_dynamics_panels}) efficiently deflects convective velocities sideways resulting in increased bulk-CZ velocities.
As $\mP$ grows, the velocities have access to an extended PZ in which to buoyantly break before deflection, resulting in slightly lower bulk velocities.
A similar trend of $\xi$ decreasing as $\mP$ increases can be seen.
Recall that smaller values of $\xi$ indicate the dissipative dynamics are rather different in the PZ and CZ.
As the size of the PZ grows, the dynamical structures of the PZ shift from what is found in the CZ, and so $\xi$ shrinks.

@@

We find that the height of the penetration zone is weakly dependent on $\mS$.
In the left panel of Fig.~\ref{fig:parameters_vs_s}, we plot the penetration height of a few discontinuous-$k$ simulations with $\mP_D = 4$ and $\mR = 400$ but with different values of $\mS$.
We find that the mean penetration height $\delta_{0.5}$ varies only weakly with changing $\mS$, but that the values of $\delta_{0.1}$ and $\delta_{0.9}$ vary more strongly.
In other words, the transition region in which $\justgrad$ varies from $\gradad$ in the PZ to $\gradrad$ in the RZ becomes narrower as $\mS$ increases.
To quantify this effect, we plot $\delta_{0.9} - \delta_{0.1}$ in the righthand panel of Fig.~\ref{fig:parameters_vs_s}.
We find that the width of this region varies according to a $\mS^{-1/2}$ scaling law, reminiscent of the pure-overshoot law described by \citet{korre_etal_2019}.
%This suggests that the evolved profile of a convecting region can be described by a penetration zone (described by e.g., $\mP$, $f$, and $\xi$) with a thin overshooting region (described by $\mS$) within the transition between the PZ and RZ.

Note that if the enstrophy, $\omega^2$ in the convection zone exceeds the value of the square buoyancy frequency $N^2$ in the radiative zone, the gravity waves in the RZ became nonlinear.
As a result, we have restricted the simulations in this study to relatively large (yet modest compared to astrophysical values) of $10^{2} \leq \mS < 10^4$ in order to ensure $N^2 > \omega^2$ even in our highest enstrophy simulations.

>>>>

\begin{figure}[t!]
\centering
\includegraphics[width=\columnwidth]{theory_profiles.pdf}
\caption{
Temporally- and horizontally-averaged profiles from Eqn.~\ref{eqn:kinetic_energy_1D} in an evolved simulation.
The vertical dashed line corresponds to the Schwarzschild CZ boundary, the vertical solid line corresponds to the top of the PZ.
(upper) Kinetic energy fluxes $\bar{\mathcal{F}}$, which go to zero at the bottom boundary and the top of the PZ.
(bottom) Source terms from Eqn.~\ref{eqn:kinetic_energy_1D} normalized by the maximum of $\overline{\mathcal{B}}$ ($\bar{\mathcal{F}}$ in the upper panel is similarly normalized).
The buoyancy source $\bar{\mathcal{B}}$ changes sign at the Schwarzschild boundary, and $\bar{\Phi}$ is positive-definite.
\label{fig:theory_profiles}
}
\end{figure}

@@

The average convective velocity depends on the magnitude of the convective flux, $\angles{\vec{|u|}} \approx F_H^{1/3} = (Q_{\rm{mag}}\Delta_H)^{1/3}$.
The characteristic convective frequency is ${f_{\rm{conv}} = \angles{\vec{|u|}} / L_s}$.
Empirically we find that for our choice of parameters, $\angles{\vec{|u|}} \approx 1$, so going forward we define $f_{\rm{conv}} = 1$.
The stiffness is defined,
\begin{equation}
\mS \equiv \frac{N^2}{f_{\rm{conv}}^2} = N^2,
\label{eqn:stiffness}
\end{equation}
where $N^2$ is the \brunt$\,$frequency in the radiative zone.
In our nondimensionalization, $N^2 = \gradad - \gradrad$.
We use $\mS$ as a control parameter.

Aside from $\mS$ and $\mP$, the two remaining control parameters $\mR$ and $\Pran$ determine the properties of the turbulence.
The value of $\mR$ corresponds to the value of the Reynolds number $\rm{Re} = \mR |\vec{u}|$, and we will vary $\mR$.
Astrophysical convection exists in the limit of $\Pran \ll 1$ \citep{garaud2021}; in this work we choose a modest value of $\Pran = 0.5$ which slightly separates the thermal and viscous scales while still allowing us to achieve convection with large Reynolds and P\'{e}clet numbers.

\subsection{Case I: Discontinuous flux}
Most of the simulations in this paper have a discontinuous convective flux at the Schwarzschild convective boundary.
We achieve this by constructing a discontinuous radiative conductivity,
\begin{equation}
k = \begin{cases}
k_{\rm{CZ}}	&	z < 1 \\
k_{\rm{RZ}} &	z \geq 1
\end{cases},
\label{eqn:sim_discontinuous_k}
\end{equation}
where CZ refers to the convection zone and RZ refers to the radiative zone (some of which will be occupied by the penetrative zone PZ).
Using $\mS$ and $\mP_D$ as inputs and specifying the radiative flux at the bottom boundary and in the RZ defines this system\footnote{
We solve the system of equations $\mS = (\gradad - \gradrad)/f_{\rm{conv}}^2$, $\mP = F_H/(k_{\rm{RZ}}[\gradad - \gradrad])$, $F_{\rm{bot}} = k_{\rm{CZ}}\gradad$, and ${F_{\rm{bot}} + F_H = k_{\rm{RZ}}\gradrad}$ to arrive at Eqns.~\ref{eqn:discontinuous_constants}.
%In the dimensional equations, $N^2 = |\alpha| g (\gradad - \gradrad)$, but we have nondimensionalized out the $\alpha$ and $g$.
},
\begin{equation}
\begin{split}
&k_{\rm{RZ}} = \frac{F_H}{f_{\rm{conv}}^2\mS\mP_D},\\
&k_{\rm{CZ}} = k_{\rm{RZ}}\frac{\mu}{1 + \mu + \mP_D^{-1}},\\
&\gradad = f_{\rm{conv}}^{2}\mS\mP_D(1 + \mu + \mP_D^{-1}),\\
&\gradrad = \gradad - f_{\rm{conv}}^{2}\mS.
\label{eqn:discontinuous_constants}
\end{split}
\end{equation}

@@

\subsection{Case II: Piecewise linear flux}
We also study simulations where the flux's gradient may be discontinuous at the Schwarzschild convective boundary.
We achieve this by constructing a radiative conductivity with a piecewise discontinuous gradient,
\begin{equation}
\partial_z k = \partial_z k_0
\begin{cases}
1	&	z < 1 \\
\mP_L^{-1} &	z \geq 1
\end{cases}
\label{eqn:sim_linear_k}
\end{equation}
Since $k$ varies with height, formally the values of $\mS$ and $\mP$ also vary with height; we specify their values at $z = 2$.
By this choice\footnote{
We solve the system of equations where ${F_{\rm{bot}} = k_{\rm{bot}}\gradad}$, ${F_{\rm{bot}} + F_H = k_{\rm{ad}}\gradad}$, ${k_{\rm{ad}} = k_{\rm{bot}} + \partial_z k_0 L_s}$, ${\mS = (\gradad - \justgrad_{\mathrm{rad},z=2L_s})/f_{\rm{conv}}^2}$, and ${\gradrad = F_{\rm{tot}}/k(z)}$.
}, we require
\begin{equation}
\partial_z k_0 = \frac{F_{H}}{f_{\rm{conv}}^2L_s \mS \psi},\,\,
k_b = \frac{F_H \mu}{f_{\rm{conv}}^2\mS\psi},\,\,
\gradad = f_{\rm{conv}}^2 \mS \psi,
\end{equation}
where $\psi \equiv 1 + \mP_L(1 + \mu)$.
We will study one sweep through $\mP_L$ space at fixed $\mR$ and $\mS$.
According to Eqn.~\ref{eqn:linear_prediction}, we expect $\delta_p \propto \mP_L^{1/2}$.

@@

\begin{figure*}[t]
\centering
\includegraphics[width=\textwidth]{time_evolution.pdf}
\caption{
(left top panel) The PZ height $\delta_{0.5}$ vs.~time.
We also show the time evolution of $f$ (left middle panel, defined in Eqn.~\ref{eqn:f_defn}) and $\xi$ (left bottom panel, defined in Eqn.~\ref{eqn:xi_defn}).
The vertical lines denote the times at which the traces first converge to within 1\% of their final values, which are denoted by solid horizontal lines.
(right panel) The vertical profile of $\justgrad/\gradad$ is plotted against height at regular time intervals.
The line color denotes the time, following the time traces in the left panels.
The constant value of $\gradad$ is denoted by the horizontal dashed grey line, and the value of $\gradrad$ is denoted by the solid grey line.
The location of the Schwarzschild convective boundary is displayed as a vertical dashed black line.
The top-of-PZ departure points (Eqn.~\ref{eqn:delta_p_measures}) are plotted over the profile evolution ($\delta_{0.1}$ and $\delta_{0.9}$ as red lines, $\delta_{0.5}$ as black lines).
\label{fig:time_evolution}
}
\end{figure*}

@@

\begin{figure*}[t]
\centering
\includegraphics[width=\textwidth]{parameters_vs_p.pdf}
\caption{
Results from simulations with a Schwarzschild boundary characterized by a discontinuous conductivity (left, Case I, $k$ defined by Eqn.~\ref{eqn:sim_discontinuous_k}) and with a discontinuous conductivity gradient (right, Case II, $k$ defined by Eqn.~\ref{eqn:sim_linear_k}).
The top panels show the penetration height according to Eqn.~\ref{eqn:delta_p_measures}.
The Case I penetration heights (upper left) vary linearly with $\mP$, in line with the prediction of Eqn.~\ref{eqn:discontinuous_prediction}.
The Case II penetration heights (upper right) vary like $\sqrt{\mP}$, in line with the prediction of Eqn.~\ref{eqn:linear_prediction}.
In the middle panels, we measure $f$ according to Eqn.~\ref{eqn:f_defn}.
We find values of $f \in [0.6, 0.9]$, and changes in $f$ are secondary to changes in $\mP$ for determining penetration heights.
In the bottom panels, we measure $\xi$ according to Eqn.~\ref{eqn:xi_defn}.
We find characteristic values of $\xi \in [0.5, 0.75]$, suggesting that the falloff of the $\bar{\Phi}$ in the PZ is well described by a linear function (at high $\mP$ when $\xi = 1/2$), or by a cubic function (at low $\mP$ when $\xi \approx 3/4$).
\label{fig:parameters_vs_p}
}
\end{figure*}

@@

We now describe the results of the 3D dynamical simulations described in the previous section.
Fig.~\ref{fig:vertical_dynamics_panels} displays the dynamics in one of these simulations.
In this section, we quantitatively compare our simulations to the theory of Sec.~\ref{sec:theory} using temporally averaged measures.

@@

In Fig.~\ref{fig:time_evolution}, we show the time evolution of a Case I (discontinuous conductivity) simulation with $\mR = 400$, $\mS = 10^3$, and $\mP_D = 4$ whose initial temperature profile sets $\justgrad = \gradad$ in the convection zone ($z \lesssim 1$) and $\justgrad = \gradrad$ in the radiative zone ($z \gtrsim 1$).
In the top left panel, we display the height of the penetrative region $\delta_{\rm{0.5}}$ vs.~time.
This region initially grows quickly over hundreds of freefall times, but this evolution slows down; reaching the final equilibrium takes tens of thousands of freefall times.
The evolution of the other parameters in our theory ($f$, $\xi$) are shown in the middle and bottom left panels of Fig.~\ref{fig:time_evolution}.
We plot the rolling mean, averaged over 200 freefall time units. 
We see that the values of $f$ and $\xi$ reach their final values ($f \approx 0.67$, $\xi \approx 0.58$) faster than the penetration zone evolves to its full height.
We quantify this fast evolution by plotting vertical lines in each of the left three panels corresponding to the first time at which the rolling average converges to within 1\% of its equilibrated value.
The equilibrated value is averaged over the final 1000 freefall times of the simulation and plotted as a grey horizontal line.
The evolved value of $f$ indicates that roughly 2/3 of the buoyancy driving is dissipated in the bulk CZ, so that 1/3 is available for PZ dissipation and negative buoyancy work.
The evolved value of $\xi$ indicates that the shape of dissipation in the PZ is slightly steeper than linear.

In the right panel of Fig.~\ref{fig:time_evolution}, we plot the profile of $\justgrad/\gradad$ in our simulation at regular time intervals, where the color of the profile corresponds to time, as in the left panels.
$\gradad$ is plotted as a dashed horizontal line while $\gradrad$ is plotted as a grey solid line which decreases with height around $z \approx 1$ and satures to a constant above $z \gtrsim 1.1$.
The location of the Schwarzschild boundary, $L_s$, is overplotted as a black vertical dashed line.
We note that the Schwarzschild boundary does not move over the course of our simulation, so the extention of the convection zone past this point is true penetration and not the result of entrainment-induced changes in the Schwarzschild (or Ledoux) convective boundaries.
The traces of $\delta_{0.1}$ and $\delta_{0.9}$ are overplotted as red lines while that of $\delta_{0.5}$ is plotted as a black line.
We see that the fast initial evolution establishes a sizeable PZ (denoted by purple $\justgrad$ profiles), but its final equilibration takes much longer (indicated by the separation between the purple, green, and yellow profiles decreasing over time).

This long evolution is computationally expensive; for this modest simulation (256x64$^2$ coefficients), this evolution takes roughly 20 days on 1024 cores for a total of $\sim$500,000 cpu-hours.
It is not feasible to perform simulations of this length for a full parameter space study, and so we accelerate the evolution of most of the simulations in this work.
To do so, we take advantage of the nearly monotonic nature of the evolution of $\delp$ vs.~time displayed in Fig.~\ref{fig:time_evolution}.
We measure the instantaneous values of $(\delta_{0.1}, \delta_{0.5}, \delta_{0.9})$, as well as their instantaneous time derivatives.
Using these values, we take a large ``time step'' forward, advancing the values of $\delp$ according to their current trend.
While doing so, we preserve the width of the transition from the PZ to the RZ, and we also adjust the solution so that $\justgrad = \gradrad$ in the RZ, effectively equilibrating the RZ instantaneously.
In other words, we reinitialize the simulation's temperature profile with a better guess at its evolved state based on its current dynamical evolution.
For details on how this procedure is carried out, see Appendix \ref{app:accelerated_evolution}.

\begin{figure*}[t]
\centering
\includegraphics{parameters_vs_s.pdf}
\caption{
(Left panel) Penetration heights are shown as a function of stiffness for Case I simulations with a discontinuous conductivity.
While the width of the transition layer from the adiabatic PZ to the stable RZ shrinks as a function of $\mS$, the mean penetration height ($\delta_{0.5}$) is roughly constant.
(Right panel) The width of the thermal transition layer ($\delta_{0.9} - \delta_{0.1}$) is shown as a function of stiffness.
We roughly observe a $\mS^{-1/2}$ scaling, similar to that expected by e.g., \citet{korre_etal_2019}.
\label{fig:parameters_vs_s}
}
\end{figure*}

\subsection{Dependence on $\mP$}
We find that the height of the penetration zone is strongly dependent on $\mP$.
In the upper two panels of Fig.~\ref{fig:parameters_vs_p}, we plot the penetration height ($\delta_{0.1}$, $\delta_{0.5}$, $\delta_{0.9}$ from Eq.~\ref{eqn:delta_p_measures}) from Case I simulations (discontinuous $k$, upper left) and Case II simulations (discontinuous $\partial_z k$, upper right).
The fixed values of $\mR$ and $\mS$ are shown above these panels.
We find that the leading-order $\mP$ scaling predictions of Eqns.~\ref{eqn:discontinuous_prediction} \& \ref{eqn:linear_prediction} describe the data extremely well (orange lines).
At small values of $\mP$ we see somewhat weaker scalings than these predictions, because the profiles of $k$ and $\partial_z k$ are not truly discontinuous but jump from one value in the CZ to another in the RZ over a finite width (see e.g., the $\gradrad$ profile in Figs.~\ref{fig:grad_profiles} \& \ref{fig:time_evolution} and Sec.~\ref{sct:numerics}).
At large values of $\mP$, the penetration height falls off of these predicted scaling laws.
In this regime, dissipation dominates over buoyancy in the PZ, so the PZ height saturates.

The middle and bottom panels of Fig.~\ref{fig:parameters_vs_p} demonstrate that that $f$ and $\xi$ are to leading order constant with $\mP$.
However, we find that $f$ has slightly smaller values in the Case I simulations (left) than in the Case II simulations (right).
We measure characteristic values of $f \in [0.6, 0.9]$, signifying that 60-90\% of the buoyant work is balanced by dissipation in the convection zone, depending on the simulation.
We note a weak trend where $f$ decreases as $\mP$ increases.
As $\mP$ increases, we find that CZ velocities decrease, leading to a decrease in the dissipation rate.
When $\mP$ is small, the PZ-RZ boundary (which acts like a wall, left panel of Fig.~\ref{fig:vertical_dynamics_panels}) efficiently deflects convective velocities sideways resulting in increased bulk-CZ velocities.
As $\mP$ grows, the velocities have access to an extended PZ in which to buoyantly break before deflection, resulting in slightly lower bulk velocities.
A similar trend of $\xi$ decreasing as $\mP$ increases can be seen.
Recall that smaller values of $\xi$ indicate the dissipative dynamics are rather different in the PZ and CZ.
As the size of the PZ grows, the dynamical structures of the PZ shift from what is found in the CZ, and so $\xi$ shrinks.

@@

We find that the height of the penetration zone is weakly dependent on $\mS$.
In the left panel of Fig.~\ref{fig:parameters_vs_s}, we plot the penetration height of a few Case I simulations with $\mP_D = 4$ and $\mR = 400$ but with different values of $\mS$.
The mean penetration height $\delta_{0.5}$ varies only weakly with changing $\mS$, but that the values of $\delta_{0.1}$ and $\delta_{0.9}$ vary more strongly.
The thermal adjustment layer in which $\justgrad$ changes from $\gradad$ in the PZ to $\gradrad$ in the RZ therefore becomes narrower as $\mS$ increases.
To quantify this effect, we plot $\delta_{0.9} - \delta_{0.1}$ in the righthand panel of Fig.~\ref{fig:parameters_vs_s}.
We find that the width of this region varies roughly according to a $\mS^{-1/2}$ scaling law, reminiscent of the pure-overshoot law described by \citet{korre_etal_2019}.
%This suggests that the evolved profile of a convecting region can be described by a penetration zone (described by e.g., $\mP$, $f$, and $\xi$) with a thin overshooting region (described by $\mS$) within the transition between the PZ and RZ.
